Backward designing a reproducible framework for undergraduate data science research

### 2019-12-04 Rmd/methods.Rmd
started adding stuff for backward design

We started with the backward design principles from @wiggins2005understanding. We prioritized

>>>>

We used the backward design principles from @wiggins2005understanding 
to create a framework for undergraduate data science research. 
Following @wiggins2005understanding, we identified desired results, 
determined acceptable evidence, and planned learning experiences.

In establishing framework priorities, we categorized all terms from Figure 1 of @nolan2010computing into 3 categories: 
1. worth being familiar with 
1. important to know and do
1. enduring understanding
